Ensembler: Enabling high-throughput molecular simulations at the superfamily scale

### 2016-01-17 manuscript-post-acceptance-submission/ensembler.tex
Fix typo in Sonya's name.

% Title must be 250 characters or less.
% Please capitalize all terms in the title except conjunctions, prepositions, and articles.
\begin{flushleft}
{\Large
\textbf\newline{Ensembler: Enabling High-Throughput Molecular Simulations at the Superfamily Scale}
}
\newline
% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
\\
Daniel L. Parton\textsuperscript{1,},
Patrick B. Grinaway\textsuperscript{1},
Sonya M. Hansom\textsuperscript{1},
Kyle A. Beauchamp\textsuperscript{1},
John D. Chodera\textsuperscript{1,*},
\\
\bigskip
\bf{1} Computational Biology Program, Sloan Kettering Institute, Memorial Sloan Kettering Cancer Center, New York, NY 10065
\\
\bigskip

>>>>

% Title must be 250 characters or less.
% Please capitalize all terms in the title except conjunctions, prepositions, and articles.
\begin{flushleft}
{\Large
\textbf\newline{Ensembler: Enabling High-Throughput Molecular Simulations at the Superfamily Scale}
}
\newline
% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
\\
Daniel L.~Parton\textsuperscript{1,},
Patrick B.~Grinaway\textsuperscript{2},
Sonya M.~Hanson\textsuperscript{1},
Kyle A.~Beauchamp\textsuperscript{1},
John D.~Chodera\textsuperscript{1,*},
\\
\bigskip
\bf{1} Computational Biology Program, Sloan Kettering Institute, Memorial Sloan Kettering Cancer Center, New York, NY 10065
\\
\bf{2} Graduate Program in Physiology, Biophysics, and Systems Biology, Weill Cornell Medical College, New York, NY 10065
\\
\bigskip
